Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-05-28 presentation/presentation.tex
ppt update; animation;

% % Theme choice:
% \usetheme{Antibes}
% % \usecolortheme{beaver}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Use roboto Font (recommended)
\usepackage[sfdefault]{roboto}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Use roboto Font (recommended)
\usepackage[sfdefault]{roboto}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

@@

\logo{
    \includegraphics[height=0.3cm]{logo_KAIST.png}
    \hspace{.5cm}%
    \includegraphics[height=0.3cm]{logo_KAIST.png}
}

@@

\AtBeginSubsection[]{%
  \begin{frame}
  \vfill
  \centering
    \insertsectionhead
    \\
    \large\textbf{\insertsubsectionhead}
  \vfill
  \end{frame}
}

@@

\begin{frame}{What is Neuro–Adaptive Control?}

  \begin{block}{Neuro–Adaptive Control}
      \begin{itemize}
          \visible<+->{
            \item \textbf{Neuro–adaptive control} is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control techniques}.
          }
          \visible<+->{
            \item It is used to handle uncertainties and nonlinearity in dynamic systems \cite{Arefinia:2020aa}. 
          }
      \end{itemize}
  \end{block}

  \begin{figure}
    \includegraphics[width=0.4\textwidth]{../fig/fig5.eps}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
  \end{figure}

@@

\begin{frame}{Effectiveness of Neuro–Adaptive Control}

@@

\subsection{Limitations of Neuro–Adaptive Control}

\begin{frame}{Inherent Challenges in Neuro–Adaptive Control}

@@

\begin{frame}{Literature Review}

\begin{frame}{Research Objectives}

\subsection{Constrained Optimization Problem Formulation}

\begin{frame}{Original Problem Formulation}
  \large\textbf{Objectives}:
  \begin{itemize}
    \item Minimize the tracking error by adapting the NN weights $\estwth$.
    \item Guarantee the stability of the system and the NN weights $\estwth$.
  \end{itemize}

  \begin{figure}
    \includegraphics[width=0.5\textwidth]{figures/problem.drawio.pdf}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
  \end{figure}

  \small{
    \textit{Notations}: 
    $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{q}$: Joint position, $\estwth$: Estimated NN weights.
  }

\subsection{Stability Analysis}

\subsection{Simulation Setup}
\begin{frame}{2-Link Robotic Manipulator}

\begin{frame}{Flux}{plots}
	\begin{minipage}{0.56\textwidth}
		\begin{figure}
			\includegraphics[width=\textwidth]{assets/plot.png}
		\end{figure}
	\end{minipage}
	\hfill
	\begin{minipage}{0.38\textwidth}
		\begin{block}{Binary Softmax classifier}
			\centering
			$\sigma(\sum_i w_ix_i + b)$
		\end{block}
		\begin{exampleblock}{Loss function}
			\centering\vspace*{0.1cm}
			$L_i = -log(\frac{e^{f_{y_i}}}{\sum_j e^{f_j}})$\\[0.1cm]
			cross entropy
		\end{exampleblock}
	\end{minipage}
\end{frame}

\begin{frame}{Flux}{tables}
    \begin{table}
      \caption{Largest cities in the world (source: Wikipedia)}
      \begin{tabular}{@{} lr @{}}
        \toprule
        City & Population\\
        \midrule
        Mexico City & 20,116,842\\
        Shanghai & 19,210,000\\
        Peking & 15,796,450\\
        Istanbul & 14,160,467\\
        \bottomrule
      \end{tabular}
      \hspace*{1cm}
          \setlength\extrarowheight{3pt}
      \begin{tabular}{|lr|}
        \hline
        \rowcolor{primaryLight}\color{background}City & \color{background}Population\\
        \hline
        Mexico City & 20,116,842\\
        Shanghai & 19,210,000\\
        Peking & 15,796,450\\
        Istanbul & 14,160,467\\
        \hline
      \end{tabular}
  \end{table}
\end{frame}

\begin{frame}{Weight Norm Constraint}
  \begin{columns}[T,onlytextwidth]
    \column{0.33\textwidth}
      \textbf{Items}
      \begin{itemize}
        \item Cats \item Dogs \item Birds
      \end{itemize}

    \column{0.33\textwidth}
      \textbf{Enumerations}
      \begin{enumerate}
        \item First \item Second \item Last
      \end{enumerate}

    \column{0.33\textwidth}
      \textbf{Descriptions}
      \begin{description}
        \item[Apples] Yes \item[Oranges] No \item[Grappes] No
      \end{description}
  \end{columns}
  \let\thefootnote\relax\footnote{Note the following demo slides are directly taken from metropolis theme. Copyright 2014 Matthias Vogelgesang.\\
Give a look at https://github.com/matze/mtheme/tree/master/demo}
\end{frame}

>>>>

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Block options: Default, Alert, Example
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% % Theme choice:
% \usetheme{Antibes}
% % \usecolortheme{beaver}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Use roboto Font (recommended)
% \usepackage[sfdefault]{roboto}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

\usepackage{svg}

@@

\logo{
  \vspace{-.7cm}%
  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.jpg}
  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
  \hspace{.6cm}%
  }

@@

% \AtBeginSubsection[]{%
%   \begin{frame}
%   \vfill
%   \centering
%     \insertsectionhead
%     \\
%     \large\textbf{\insertsubsectionhead}
%   \vfill
%   \end{frame}
% }

@@

\begin{frame}{\insertsubsectionhead}{What is Neuro–Adaptive Control?}

  \textbf{Neuro–Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Neuro–adaptive control} (NAC) is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control techniques} \cite{Farrell:2006aa}.
      \item It is used to handle \textbf{uncertainties} and \textbf{nonlinearity} in dynamic systems. 
    \end{itemize}
  }

  \begin{figure}
    \includegraphics[width=0.55\textwidth]{figures/NAC.drawio.pdf}
  \end{figure}

@@

\begin{frame}{\insertsubsectionhead}{What is Neuro–Adaptive Control?}

  \textbf{Advantages of Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
      \item \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textbf{Lyapunov stability theory}.
      \item \textbf{Online Learning Capability}: NAC adapts in \textbf{real-time} to new data with stability guarantees.
      \item \textbf{Robustness}: NAC handles \textbf{uncertainties and disturbances} effectively with adaptive control techniques.
    \end{itemize}
  }

@@

\begin{frame}{\insertsubsectionhead}{Existing Challenges in NAC}

  \textbf{Challenges}
  \small{
    \begin{itemize}
      \item \textbf{Optimality}: In general, the adaptation laws are deriven with respect to the tracking error, which may not guarantee optimal performance.
      \item \textbf{Unpredictable Amplitude of NN Weights}: 
        \begin{itemize}
          \item NN weights may diverge, leading to instability.
          \item This can result in unpredictable behavior of the controller.
        \end{itemize}
      \item \textbf{Parameter Dependency}: 
    \end{itemize}
  }

  \begin{figure}
    \includegraphics[width=0.25\textwidth]{figures/KAIST-hi.png}
  \end{figure}

\subsection{Literature Review}

\begin{frame}{\insertsubsectionhead}

  In general, the NN outputs are bounded by limiting the maximum amplitude of the NN weights.

  \begin{enumerate}
    \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Projection Operator}

          \begin{itemize}
            \item Cats 
            \item Dogs 
            \item Birds
          \end{itemize}

        \column{0.49\textwidth}
          \begin{figure}
            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
          \end{figure}
      \end{columns}

      \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{$\epsilon$-modification, and $\sigma$-modification}

          \begin{itemize}
            \item Cats 
            \item Dogs 
            \item Birds
          \end{itemize}

        \column{0.49\textwidth}
          \begin{figure}
            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
          \end{figure}
      \end{columns}
  \end{enumerate}
\end{frame}

\begin{frame}{\insertsubsectionhead}

  \textbf{Objective 1: Optimality}
  \begin{itemize}
    \item Formulate a constrained optimization problem to minimize the tracking error.
    \item Guarantee the stability of the system and the NN weights.
  \end{itemize}

  \textbf{Objective 2: Stability}
  \begin{itemize}
    \item Derive an adaptation law that guarantees the stability of the system.
    \item Ensure that the NN weights remain bounded during operation.
  \end{itemize}

  \textbf{Objective 3: Boundedness of }
  \begin{itemize}
    \item Ensure the controller is robust to uncertainties and disturbances.
    \item Validate the proposed method through numerical simulations.
  \end{itemize}

\subsection{Problem Formulation}

\begin{frame}{\insertsubsectionhead}{Original Control Problem}
  \textbf{Objectives}:
  \begin{itemize}
    \item Minimize the tracking error by adapting the NN weights $\estwth$.
    \item Guarantee the stability of the system and the NN weights $\estwth$.
  \end{itemize}

  \begin{figure}
    \includegraphics[width=0.5\textwidth]{figures/problem.drawio.pdf}
    % \includesvg{figures/problem.drawio}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
  \end{figure}

  \let\thefootnote\relax\footnote{
    \textit{Notations}: 
      $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{q}$: Joint position, $\estwth$: Estimated NN weights.
      }

\begin{frame}{\insertsubsectionhead}{Equvalent Constrained Optimization Problem}

\begin{frame}{\insertsubsectionhead}{Inequality Constraint for Weight Boundedness}

\begin{frame}{\insertsubsectionhead}{Steepest Descent Method}

\end{frame}
\subsection{Stability Analysis}

\begin{frame}{\insertsubsectionhead}{Lyapunov Stability Analysis}

\subsection{Simulation Setup}
\begin{frame}{\insertsubsectionhead}{2-Link Robotic Manipulator}

\begin{frame}{Representative Simulation Results}

\begin{frame}{Box-and-Whisker Plots}

  \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{figures/BoxWhisker.drawio.png}
        \caption{Parameter dependencies of the proposed method.}
      \end{figure}

    \column{0.5\textwidth}
      \begin{table}
        \caption{Largest cities in the world (source: Wikipedia)}
        \begin{tabular}{@{} lr @{}}
          \toprule
          City & Population\\
          \midrule
          Mexico City & 20,116,842\\
          Shanghai & 19,210,000\\
          Peking & 15,796,450\\
          Istanbul & 14,160,467\\
          \bottomrule
        \end{tabular}
    \end{table}

  \end{columns}

\begin{frame}{Parameter Dependencies}

  \begin{columns}

    \column{0.33\textwidth}
      \begin{figure}      
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig9.eps}
        \caption{Weight norms of NAC-L2}
      \end{figure}

    \column{0.33\textwidth}

      \begin{figure}
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig10.eps}
        \caption{Weight norms of NAC-eMod}
      \end{figure}

    \column{0.33\textwidth}

      \begin{figure}
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig8.eps}
        \caption{Weight norms of NAC-CO}
      \end{figure}

  \end{columns}

  The weight norms of the proposed method (NAC-CO) are bounded, while ...

\begin{frame}{Parameter Dependencies}

  \begin{columns}

    \column{0.33\textwidth}
      \begin{figure}      
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig6.eps}
        \caption{Tracking error of NAC-L2}
      \end{figure}

    \column{0.33\textwidth}

      \begin{figure}
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig7.eps}
        \caption{Tracking error of NAC-eMod}
      \end{figure}

    \column{0.33\textwidth}

      \begin{figure}
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig5.eps}
        \caption{Tracking error of NAC-CO}
      \end{figure}

  \end{columns}

  The Tracking error ...

@@
